Implications of afforestation policies for global markets

### 2024-02-27 paper.Rmd
Update paper.Rmd

Table 3. Percentage change in the amount of agricultural land in 2033 with deforestation mitigation policy in place (Source: GTAP qo-Land)qo-Ag
				∆ (%)
				Agriculture
East Asia			-5.1
Southeast Asia			-2.0
Central America			-2.0
South Asia			-1.1
North Africa & the Middle East	-0.9
Sub-Saharan Africa		-0.3
China				-0.1
Russia				0.1
Brazil				0.2
Rest of South America		-1.2
West & Central Europe 		0.4
United States			0.6
Oceania				0.7
Canada				1.3
Japan				1.4

@@

Table 4. Percentage change in the amount of agricultural land in 2033 with deforestation mitigation policy in place (Source: GTAP qo-Land)qxw-Ag
				∆ (%)
				Agriculture
Japan				8.78
United States			3.49
Canada				3.13
China				1.96
Oceania				1.67
Russia				1.52
West & Central Europe 		1.16
Brazil				1.03
Rest of South America		-2.67
Sub-Saharan Africa		0.02
North Africa & the Middle East	-1.52
Central America			-5.02
Southeast Asia			-5.14
South Asia			-5.94
East Asia			-14.45

Overall, this tax policy, which results in zero net deforestation globally, has a rather significant negative economic impact on all regions except Japan and Canada who see an increase in consumer well-being of $977.1 million and $166.9 million, respectively (table 4). Consumer well-being is a measurement of equivalent variation and here measures the benefit/harm consumers experience in terms of income as a result of the policy changes. The United States, along with 10 other regions, see well-being drop by more than $1 billion. The most negatively impacted regions are South Asia (-$28.0 billion), China (-$14.5 billion), and Southeast Asia (-$13.6 billion). In total, this tax-driven policy is estimated to decrease global consumer well-being in 2033 by $92.1 billion relative to the scenario where no tax on forestland conversion was in place.

Table 4 EV
				∆ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
Brazil				-735,125,000
Rest of South America		-3,848,625,000
United States			-1,085,000,000
Russia				-1,152,375,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
West & Central Europe		-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any price impacts that are beneficial for consumers resulting from this policy, with the price of agricultural goods decreasing 0.3 percent (table 5). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.3 and 5.1 percent.

Table 5 pm
									∆ (%)				
	Agricultural Goods		Forest Products		Lumber		Paper Products		Other Non-Agricultural Goods
Oceania						1.2	0.4	0.5	0.5	0.5
China						1.1	0.4	0.4	0.4	0.4
Japan						-0.3	0.4	0.4	0.4	0.4
East Asia					5.1	0.3	0.3	0.3	0.4
Southeast Asia					2.8	0.3	0.3	0.4	0.3
South Asia					3.1	0.3	0.3	0.3	0.3
Canada						0.7	0.5	0.5	0.5	0.5
United States					0.7	0.5	0.5	0.5	0.5
Central America					2.5	0.3	0.3	0.4	0.3
Brazil						1.2	0.5	0.5	0.5	0.5
Rest of South America				2.1	0.3	0.3	0.3	0.3
West & Central Europe 				0.9	0.4	0.4	0.4	0.4
Russia						1.1	0.4	0.4	0.4	0.4
Sub-Saharan Africa				1.5	0.4	0.4	0.4	0.4
North Africa & the Middle East			2.0	0.4	0.4	0.4	0.4

>>>>

Table 3. Percentage change in the amount of agricultural goods produced in 2033 with deforestation mitigation policy in place (Source: GTAP qo-Ag)
				∆ (%)
				Agriculture
East Asia			-5.1
Southeast Asia			-2.0
Central America			-2.0
South Asia			-1.1
North Africa & the Middle East	-0.9
Sub-Saharan Africa		-0.3
China				-0.1
Russia				0.1
Brazil				0.2
Rest of South America		-1.2
West & Central Europe 		0.4
United States			0.6
Oceania				0.7
Canada				1.3
Japan				1.4

@@

Table 4. Percentage change in the amount of agricultural exports in 2033, by region, with deforestation mitigation policy in place (Source: GTAP qxw-Ag)
				∆ (%)
				Agriculture
Japan				8.78
United States			3.49
Canada				3.13
China				1.96
Oceania				1.67
Russia				1.52
West & Central Europe 		1.16
Brazil				1.03
Rest of South America		-2.67
Sub-Saharan Africa		0.02
North Africa & the Middle East	-1.52
Central America			-5.02
Southeast Asia			-5.14
South Asia			-5.94
East Asia			-14.45

Overall, this tax policy, which results in zero net deforestation globally, has a rather significant negative economic impact on all regions except Japan and Canada who see an increase in consumer well-being of $977.1 million and $166.9 million, respectively (Table 5). Consumer well-being is a measurement of equivalent variation and here measures the benefit/harm consumers experience in terms of income as a result of the policy changes. The United States, along with 10 other regions, see well-being drop by more than $1 billion. The most negatively impacted regions are South Asia (-$28.0 billion), China (-$14.5 billion), and Southeast Asia (-$13.6 billion). In total, this tax-driven policy is estimated to decrease global consumer well-being in 2033 by $92.1 billion relative to the scenario where no tax on forestland conversion was in place.

Table 5. Change in consumer well-being in 2033, by region, in dollars, with deforestation mitigation policy in place (Source: GTAP EV) 
				∆ ($)
Japan				977,125,000
Canada				166,937,500
Oceania				-169,625,000
Brazil				-735,125,000
Rest of South America		-3,848,625,000
United States			-1,085,000,000
Russia				-1,152,375,000
Central America			-4,471,500,000
North Africa & the Middle East	-5,012,125,000
East Asia			-5,065,625,000
West & Central Europe		-7,152,500,000
Sub-Saharan Africa		-7,850,500,000
Southeast Asia			-13,601,000,000
China				-14,452,000,000
South Asia			-28,024,000,000

Much of this loss in well-being may be the result of higher prices. Japan is the only nation that sees any price impacts that are beneficial for consumers resulting from this policy, with the price of agricultural goods decreasing 0.3 percent (Table 6). All other regions, for both agricultural and non-agricultural products, see prices rise between 0.3 and 5.1 percent.

Table 6. Change in market price of various goods in 2033, by region, with deforestation mitigation policy in place (Source: GTAP pm) 
									∆ (%)				
	Agricultural Goods		Forest Products		Lumber		Paper Products		Other Non-Agricultural Goods
Oceania						1.2	0.4	0.5	0.5	0.5
China						1.1	0.4	0.4	0.4	0.4
Japan						-0.3	0.4	0.4	0.4	0.4
East Asia					5.1	0.3	0.3	0.3	0.4
Southeast Asia					2.8	0.3	0.3	0.4	0.3
South Asia					3.1	0.3	0.3	0.3	0.3
Canada						0.7	0.5	0.5	0.5	0.5
United States					0.7	0.5	0.5	0.5	0.5
Central America					2.5	0.3	0.3	0.4	0.3
Brazil						1.2	0.5	0.5	0.5	0.5
Rest of South America				2.1	0.3	0.3	0.3	0.3
West & Central Europe 				0.9	0.4	0.4	0.4	0.4
Russia						1.1	0.4	0.4	0.4	0.4
Sub-Saharan Africa				1.5	0.4	0.4	0.4	0.4
North Africa & the Middle East			2.0	0.4	0.4	0.4	0.4
